Jane, John … Leslie? A Historical Method for Algorithmic Gender Prediction

### 2015-08-14 article.Rmd
Improve the line of fit

leslie_df %>%
  ggplot(aes(x = year, y = prop_female)) +
  geom_smooth() + 
  geom_point() +
  ggtitle("Gender of the name Leslie, 1820-2012") +
  xlab(NULL) + ylab("Proportion of female uses") + ylim(0, 1) +
  geom_hline(yintercept = 0.5) + 
  annotate("text", x = 1900, y = 0.45, label = "Male") +
  annotate("text", x = 1900, y = 0.55, label = "Female") +
  article_theme
```
**Figure 1: Gender of the name Leslie, 1820-2012**

>>>>

leslie_df %>%
  ggplot(aes(x = year, y = prop_female)) +
  geom_smooth(span = 0.5) + 
  geom_point() +
  ggtitle("Gender of the name Leslie, 1820-2012") +
  xlab(NULL) + ylab("Proportion of female uses") + ylim(0, 1) +
  geom_hline(yintercept = 0.5) + 
  annotate("text", x = 1900, y = 0.45, label = "Male") +
  annotate("text", x = 1900, y = 0.55, label = "Female") +
  article_theme
```
**Figure 1: Gender of the name Leslie, 1820-2012**
